---
title: "ball_tracking"
author: "Henry Guerrero-Duarte"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Libraries used
```{r}
library(dplyr)
library(ggplot2)
```



## Reading CSV file
```{r}
mydata1=read.csv("pitch_data_questionnaire.csv")
str(mydata1)
#View(mydata1)
#summary(mydata1)
```



## player_a
```{r}
#select rows where player_a appears in any column
df_a = mydata1 %>% filter_all(any_vars(. %in% c("player_a")))

#Pitches dataframes for player_b
changeup_a = df_a %>% filter_all(any_vars(. %in% c("changeup")))
curveball_a = df_a %>% filter_all(any_vars(. %in% c("curveball")))
cutter_a = df_a %>% filter_all(any_vars(. %in% c("cutter")))
four_seam_a = df_a %>% filter_all(any_vars(. %in% c("four_seam")))
sinker_a = df_a %>% filter_all(any_vars(. %in% c("sinker")))
slider_a = df_a %>% filter_all(any_vars(. %in% c("slider")))

#Finding out Unique names for Venues
unique(df_a$venue)

#Venue dataframes For Player_a
PrinceGeorge_a = df_a %>% filter_all(any_vars(. %in% c("PrinceGeorge")))
The_Diamond_a = df_a %>% filter_all(any_vars(. %in% c("The Diamond")))
CanalPark_a = df_a %>% filter_all(any_vars(. %in% c("CanalPark")))
UPMC_Park_a = df_a %>% filter_all(any_vars(. %in% c("UPMC Park")))
HadlockField_a = df_a %>% filter_all(any_vars(. %in% c("HadlockField")))
NaturalGasField_a = df_a %>% filter_all(any_vars(. %in% c("NaturalGasField")))
FNBField_a = df_a %>% filter_all(any_vars(. %in% c("FNBField")))
Delta_Dental_Stadium_a = df_a %>% filter_all(any_vars(. %in% c("Delta Dental Stadium")))

pitch_call_a = table(df_a['pitch_call'])


```



## player_b
```{r}
#select rows where player_b appears in any column
df_b = mydata1 %>% filter_all(any_vars(. %in% c("player_b")))

#Pitches dataframes for player_b
changeup_b = df_b %>% filter_all(any_vars(. %in% c("changeup")))
curveball_b = df_b %>% filter_all(any_vars(. %in% c("curveball")))
slider_b = df_b %>% filter_all(any_vars(. %in% c("slider")))
four_seam_b = df_b %>% filter_all(any_vars(. %in% c("four_seam")))

#Finding out Unique names for Venues
unique(df_b$venue)

#Venue dataframes For Player_b
Cheney_Stadium_b = df_b %>% filter_all(any_vars(. %in% c("Cheney Stadium")))
Las_Vegas_Ballpark_b = df_b %>% filter_all(any_vars(. %in% c("Las Vegas Ballpark")))
Sutter_Health_Park_b = df_b %>% filter_all(any_vars(. %in% c("Sutter Health Park")))
Greater_Nevada_Field_b = df_b %>% filter_all(any_vars(. %in% c("Greater Nevada Field")))
Smiths_Ballpark_b = df_b %>% filter_all(any_vars(. %in% c("Smith's Ballpark")))
Southwest_University_Park_b = df_b %>% filter_all(any_vars(. %in% c("Southwest University Park")))
Dell_Diamond_b = df_b %>% filter_all(any_vars(. %in% c("Dell Diamond")))
Isotopes_Park_b = df_b %>% filter_all(any_vars(. %in% c("Isotopes Park")))
Chickasaw_Bricktown_Ballpark_b = df_b %>% filter_all(any_vars(. %in% c("Chickasaw Bricktown Ballpark")))


#data frame for pitch_call_b
pitch_call_b = table(df_b['pitch_call'])

```


## Creating Coordniates for batters box
```{r}
x <- c(-.95,.95,.95,-.95,-.95)
z <- c(1.6,1.6,3.5,3.5,1.6)

#store in data frame
sz <- tibble(x,z) 
```


###################################   Player A Heat maps ###############################################


## player_a Pitches( changeup, curveball, cutter, four_seam, sinker, slider) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = df_a,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( changeup) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = changeup_a,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( curveball) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = curveball_a,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( cutter) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = cutter_a,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( four_seam) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = four_seam_a,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( sinker) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = sinker_a,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( slider) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = slider_a,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```


###################################   Player B Heat maps ################################################

## player_b Pitches( changeup, curveball, four_seam, slider) Heat Map   
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = df_b,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( changeup) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = changeup_b,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( curveball) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = curveball_b,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( four_seam) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = four_seam_b,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( slider) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = slider_b,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

### Player A Performance

```{r}
# Create data for the labels and Pie Chart


lbl <- c("Ball called", "Foul_ball", "Hit_by_pitch", "In_play","Strike_called","Strike_swinging")
x <- pitch_call_a


piepercent<- round(100*x/sum(x), 1)

# Give the chart file a name.
png(file = "player_a_performance.jpg")

# Plot the chart.
pie(x, labels = piepercent, main = "Player_a_Performance",col = rainbow(length(x)))
legend("topright", c("Ball called", "Foul_ball", "Hit_by_pitch", "In_play","Strike_called","Strike_swinging"), cex = 0.8,
   fill = rainbow(length(x)))

# Save the file.
dev.off()

```


### Player B Performance

```{r}
# Create data for the labels and Pie Chart

lbl <- c("Ball called", "Foul_ball", "Hit_by_pitch", "In_play","Strike_called","Strike_swinging")
x <- pitch_call_b


piepercent<- round(100*x/sum(x), 1)

# Give the chart file a name.
png(file = "player_b_performance.jpg")

# Plot the chart.
pie(x, labels = piepercent, main = "Player_b_Performance",col = rainbow(length(x)))
legend("topright", c("Ball called", "Foul_ball", "Hit_by_pitch", "In_play","Strike_called","Strike_swinging"), cex = 0.8,
   fill = rainbow(length(x)))

# Save the file.
dev.off()

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
