---
title: "ball_tracking"
author: "Henry Guerrero-Duarte"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Libraries used
```{r}
library(dplyr)
library(ggplot2)
```



## Reading CSV file
```{r}
mydata1=read.csv("pitch_data_questionnaire.csv")
str(mydata1)
#View(mydata1)
#summary(mydata1)
```



## player_a
```{r}
#select rows where player_a appears in any column
#df_a = mydata1 %>% filter_all(any_vars(. %in% c("player_a")))

#Pitches dataframes for player_b
#changeup_a = df_a %>% filter_all(any_vars(. %in% c("changeup")))
#curveball_a = df_a %>% filter_all(any_vars(. %in% c("curveball")))
#cutter_a = df_a %>% filter_all(any_vars(. %in% c("cutter")))
#four_seam_a = df_a %>% filter_all(any_vars(. %in% c("four_seam")))
#sinker_a = df_a %>% filter_all(any_vars(. %in% c("sinker")))
#slider_a = df_a %>% filter_all(any_vars(. %in% c("slider")))

#Finding out Unique names for Venues
#unique(df_a$venue)

#Venue dataframes For Player_a
#PrinceGeorge_a = df_a %>% filter_all(any_vars(. %in% c("PrinceGeorge")))
#The_Diamond_a = df_a %>% filter_all(any_vars(. %in% c("The Diamond")))
#CanalPark_a = df_a %>% filter_all(any_vars(. %in% c("CanalPark")))
#UPMC_Park_a = df_a %>% filter_all(any_vars(. %in% c("UPMC Park")))
#HadlockField_a = df_a %>% filter_all(any_vars(. %in% c("HadlockField")))
#NaturalGasField_a = df_a %>% filter_all(any_vars(. %in% c("NaturalGasField")))
#FNBField_a = df_a %>% filter_all(any_vars(. %in% c("FNBField")))
#Delta_Dental_Stadium_a = df_a %>% filter_all(any_vars(. %in% c("Delta Dental Stadium")))

#Finding out Unique names for Venues
#unique(CanalPark_a$pitch_call)

#Count the Number of Occurrences 
#table(CanalPark_a['pitch_call'])
#table(CanalPark_a['play_result'])

CanalPark_a$fieldperf <- paste(CanalPark_a$pitch_call,CanalPark_a$play_result)
summary(CanalPark_a$fieldperf)




```



## player_b
```{r}
#select rows where player_b appears in any column
df_b = mydata1 %>% filter_all(any_vars(. %in% c("player_b")))

#Pitches dataframes for player_b
#changeup_b = df_b %>% filter_all(any_vars(. %in% c("changeup")))
#curveball_b = df_b %>% filter_all(any_vars(. %in% c("curveball")))
#slider_b = df_b %>% filter_all(any_vars(. %in% c("slider")))
#four_seam_b = df_b %>% filter_all(any_vars(. %in% c("four_seam")))

#Finding out Unique names for Venues
unique(df_b$venue)

#Venue dataframes For Player_b
Cheney_Stadium_b = df_b %>% filter_all(any_vars(. %in% c("Cheney Stadium")))
Las_Vegas_Ballpark_b = df_b %>% filter_all(any_vars(. %in% c("Las Vegas Ballpark")))
Sutter_Health_Park_b = df_b %>% filter_all(any_vars(. %in% c("Sutter Health Park")))
Greater_Nevada_Field_b = df_b %>% filter_all(any_vars(. %in% c("Greater Nevada Field")))
Smiths_Ballpark_b = df_b %>% filter_all(any_vars(. %in% c("Smith's Ballpark")))
Southwest_University_Park_b = df_b %>% filter_all(any_vars(. %in% c("Southwest University Park")))
Dell_Diamond_b = df_b %>% filter_all(any_vars(. %in% c("Dell Diamond")))
Isotopes_Park_b = df_b %>% filter_all(any_vars(. %in% c("Isotopes Park")))
Chickasaw_Bricktown_Ballpark_b = df_b %>% filter_all(any_vars(. %in% c("Chickasaw Bricktown Ballpark")))

```



## Creating Coordniates for batters box
```{r}
x <- c(-.95,.95,.95,-.95,-.95)
z <- c(1.6,1.6,3.5,3.5,1.6)

#store in data frame
sz <- tibble(x,z) 
```


###################################   Player A Heat maps ###############################################


## player_a Pitches( changeup, curveball, cutter, four_seam, sinker, slider) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = df_a,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( changeup) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = changeup_a,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( curveball) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = curveball_a,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( cutter) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = cutter_a,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( four_seam) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = four_seam_a,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( sinker) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = sinker_a,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( slider) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = slider_a,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```


###################################   Player B Heat maps ################################################

## player_b Pitches( changeup, curveball, four_seam, slider) Heat Map   
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = df_b,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( changeup) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = changeup_b,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( curveball) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = curveball_b,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( four_seam) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = four_seam_b,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

## player_a Pitches( slider) Heat map
```{r}
ggplot()+
  geom_path(data = sz, aes(x=x, y=z))+
  coord_equal()+
  xlab("feet from home plate")+
  ylab("feet above the ground")+
  geom_point(data = slider_b,aes(x=plate_loc_side,y=plate_loc_height,size=rel_speed,color=pitch_type))+
  scale_size(range = c(0.01,3))
```

###################################   Player A Performance at each Venue ################################



```{r}
# Get the library.
library(plotrix)

# Create data for the graph.

lbl <- c("ball_called", "foul_ball", "hit_by_pitch", "in_play","strike_called","strike_swinging")

# Give the chart file a name.
png(file = "player_a_pie_chart.jpg")

# Plot the chart.
pie3D(pitch_call_a,labels = lbl,explode = 0.1, main = "player_a_pie_chart ")

# Save the file.
dev.off()

```



###################################   Player B Performance at each Venue ################################

```{r}

# Get the library.
library(plotrix)

# Create data for the graph.

lbl <- c("ball_called", "foul_ball", "hit_by_pitch", "in_play","strike_called","strike_swinging")

# Give the chart file a name.
png(file = "player_b_pie_chart.jpg")

# Plot the chart.
pie3D(pitch_call_b,labels = lbl,explode = 0.1, main = "player_a_pie_chart ")

# Save the file.
dev.off()


```





Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
